% 6.1
% Introduction

For the past several years many lattice groups have been involved in studying strongly-coupled near-conformal gauge--fermion systems.
Some of these models may be candidates for new physics beyond the standard model, while others are simply interesting non-perturbative quantum field theories.
Because the dynamics of these lattice systems are unfamiliar, it is important to study them with several complementary techniques.
Not only does this allow consistency checks, it can also provide information about the most efficient and reliable methods to investigate near-conformal lattice theories.

Monte Carlo Renormalization Group (MCRG) two-lattice matching is one of several analysis tools that we are using to investigate SU(3) gauge theories with many massless fermion flavors.
This technique predicts the step-scaling function $s_b$ in the bare parameter space.
In a previous work~\cite{Petropoulos:2012mg} we proposed an improved MCRG method that exploits the Wilson flow to obtain a bare step-scaling function that corresponds to a unique discrete \be function.
We briefly review our Wilson-flow-optimized MCRG (WMCRG) procedure in Sections~\ref{sec:mcrg}--\ref{sec:wmcrg}.
It is important to note that we are investigating a potential infrared fixed point (IRFP) where the coupling is irrelevant: its running slows and eventually stops.
This is challenging to distinguish from a near-conformal system where the gauge coupling runs slowly but does not flow to an IRFP.
The observation of a backward flow that survives extrapolation to the infinite-volume limit could provide a clean signal.
In \secref{sec:results} we report WMCRG results for SU(3) gauge theory with $N_f = 12$ flavors of massless fermions in the fundamental representation.

This 12-flavor model has been studied by many groups, including Refs.~\cite{Appelquist:2009ty, Deuzeman:2009mh, Fodor:2011tu, Appelquist:2011dp, Hasenfratz:2011xn, DeGrand:2011cu, Cheng:2011ic, Jin:2012dw, Lin:2012iw, Aoki:2012eq, Fodor:2012uw, Fodor:2012et, Itou:2012qn, Cheng:2013eu, Aoki:2013pca, Hasenfratz:2013uha, Hasenfratz:2013eka, Cheng:2013bca}.
Using new ensembles of 12-flavor gauge configurations generated with exactly massless fermions, our improved WMCRG technique predicts a conformal IRFP where the step-scaling function vanishes.
As with every method, it is essential to study the systematic effects.
For WMCRG the most important systematic effects are due to the finite volume and limited number of blocking steps.
While we are not able to carry out a rigorous infinite-volume extrapolation, the observed zero of the bare step-scaling function is present for all investigated lattice volumes and renormalization schemes, and agrees with the earlier MCRG results of \refcite{Hasenfratz:2011xn}.
The results of our complementary $N_f = 12$ investigations of finite-temperature phase transitions~\cite{Schaich:2012fr, Hasenfratz:2013uha}, the Dirac eigenmode number~\cite{Cheng:2013eu, Cheng:2013bca}, and finite-size scaling~\cite{Hasenfratz:2013eka} are also consistent with the existence of an infrared fixed point and IR conformality.
