\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amsmath}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{cancel}
\usepackage{mystyle}
\usepackage{slashed}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{feynmp-auto}
\unitlength = 1mm

% Laziness shortcuts
\newcommand{\al}{\ensuremath{\alpha} }
\newcommand{\be}{\ensuremath{\beta} }
\newcommand{\ga}{\ensuremath{\gamma} }
\newcommand{\De}{\ensuremath{\Delta} }
\newcommand{\lsim}{\ensuremath{\lesssim} }
\newcommand{\vev}[1]{\ensuremath{\left\langle #1 \right\rangle} }
\newcommand{\X}{\ensuremath{\!\times\!} }
\newcommand{\Sb}{\ensuremath{\cancel{S^4}} }
\newcommand{\MSbar}{\ensuremath{\overline{\textrm{MS}}} }
\newcommand{\refcite}[1]{Ref.~\cite{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\cnum}[1]{chapter_#1}
\newcommand{\cO}{\ensuremath{\mathcal O} }
\newcommand{\cN}{\ensuremath{\mathcal N} }
\newcommand{\cC}{\ensuremath{\mathcal C} }
\newcommand{\gGF}{\ensuremath{g_{\rm GF}^2} }
\newcommand{\gc}{\ensuremath{g_c^2} }
\newcommand{\de}{\ensuremath{\delta} }
\newcommand{\eq}[1]{eq.~\ref{#1}}
\newcommand{\gtGF}{\ensuremath{\widetilde g_{\rm GF}^2} }
\newcommand{\gtopt}{\ensuremath{\widetilde g_{\rm opt}^2} }
\newcommand{\topt}{\ensuremath{\tau_{\rm opt}} }
\newcommand{\gtc}{\ensuremath{\widetilde g_c^2} }
\newcommand{\gstar}{\ensuremath{g_{\star}^2} }
\newcommand{\Lagr}{\mathcal{L}}

%\newcommand{\MSbar}{\ensuremath{\overline{\mbox{MS}}} }
% ------------------------------------------------------------------


%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Studies with Improved Renormalization Group Techniques}

\author{Gregory James}{Petropoulos}

\otherdegrees{B.S., University of Connecticut, 2010 \\
	      M.S., University of Colorado, 2013}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Physics}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Physics}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Anna Hasenfratz}			%  #2 {name}

\reader{Prof.~Thomas DeGrand}		        %  2nd person to sign thesis
%\readerThree{Prof.~Ethan Neil}		        %  3rd person to sign thesis
%\readerFour{Prof.~Senarath de Alwis}		  %  4th person to sign thesis
%\readerFive{Prof.~Thomas A. Manteuffel}		%  5th person to sign thesis

\abstract{  \OnePageChapter	% because it is very short
  The discovery of the Higgs Boson at the Large Hadron Collider in 2012 completes the Electroweak Sector of the Standard Model.
  Although the Standard Model is complete with a scalar Higgs, the hierarchy problem raises concerns about a scalar mechanism for electroweak symmetry breaking.
  Strongly interacting gauge-fermion systems that break electroweak symmetry are an interesting alternative because they provide an ultraviolet completion to the Standard Model.
  The only reliable technique to study strongly interacting quantum field theories is a numerical technique called Lattice Gauge Theory.

  In this dissertation I describe lattice studies of SU(3) gauge theories with many flavors of chiral fermions in the fundamental representation.
  This is part of a larger effort to find a viable composite Higgs model.
  I employ lattice renormalization group techniques to study the infrared properties of these theories.
  Additionally I show how it is possible to improve traditional techniques with an optimization step.
  Results indicate that SU(3) 12 flavors is a conformal field theory while the 8 flavor theory is confining and spontaneously breaks chiral symmetry.
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
  To my parents James and Judy Petropoulos.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
  This thesis would not be possible without the help of those around me.
  My advisor,  Anna Hasenfratz, deserves special thanks for her support and encouragement throughout my PhD.
  I also need to thank my committee for their insights and help with this thesis.
  I would also like to thank David Schaich and Yuzhi Liu who were both postdoctoral researchers in our group who helped me tremendously.
  I want to thank all of my teachers throughout the years: especially Tom Blum for advising me as an undergraduate and Keith Gregorian-Michaelsen for teaching me physics in high school.
  Additionally, I thank Anqi Cheng, my officemates, and classmates for countless discussions and collaboration.
  Finally, I thank my friends and family for being supportive of me, especially when life was stressful.

  This thesis was supported by an award from the Department of Energy (DOE) Office of Science Graduate Fellowship Program (DOE SCGF).
  The DOE SCGF Program was made possible in part by the American Recovery and Reinvestment Act of 2009.
  The DOE SCGF program is administered by the Oak Ridge Institute for Science and Education for the DOE.
  ORISE is managed by Oak Ridge Associated Universities (ORAU) under DOE contract number DE- AC05-06OR23100. 
  All opinions expressed in this presentation are the author's and do not necessarily reflect the policies and views of DOE, ORAU, or ORISE.
	}

%\ToCisShort	% use this only for 1-page Table of Contents

%\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

  \include{chapter_1/chapter_1}
  \include{chapter_2/chapter_2}
  \include{chapter_3/chapter_3}
  \include{chapter_4/chapter_4}
  \include{chapter_5/chapter_5}
  \include{chapter_6/chapter_6}
  \include{chapter_7/chapter_7}

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
  \bibliographystyle{plain}	% or "siam", or "alpha", etc.
  \nocite{*}		% list all refs in database, cited or not
  %\bibliography{refs}		% Bib database in "refs.bib"
  \bibliography{ds_ref}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
  \appendix
  %\input appendix/abbreviations.tex
  %\input appendix/appendixB.tex

\end{document}
